
\begin{thebibliography}{8}

\bibitem{Lawless}
Lawless and Jerald (2002), Statistical Models and Methods for Lifetime Data (Second ed.) ,p16--22. 
\bibitem{weibull}
Chin-Diew and Lai (2006), Weibull Distributions and Their Applications.
 \bibitem{deep_learning_book}
 Iaan Goodfellow, Yoshua Bengio and Aaron Courville (2015), deep learning, p-210. 
 \bibitem{Hands-On}
Niloy Purkait (2019), Hands-On Neural Networks with Keras.
 \bibitem{deep_learning_book_p410}
 Iaan Goodfellow, Yoshua Bengio and Aaron Courville (2015), deep learning, p-410. 
\bibitem{WTTE-RNN}
EGIL MARTINSSON (2016) A model for sequential prediction of time-to-event in the case
\bibitem{logistic}
Xuhui Shao and Lexin Li (2011), Data-driven Multi-touch Attribution Models. 
\bibitem{lift}
Jian Xu∗, Xuhui Shao, Jianjie Ma, Kuang-chih Lee, Hang Qi and Quan Lu (2016), Lift-Based Bidding in Ad Selection.
\bibitem{additive}
Junchi Yan123, Chao Zhang2, Hongyuan Zha14, Min Gong2, Changhua Sun2, Jin Huang2, Stephen Chu2 and Xiaokang Yang3 (2015) On Machine Learning towards Predictive Sales Pipeline Analytics. 
\bibitem{survival_sol}
Ya Zhang, Yi Wei, Jianbiao Ren (2014) ,Multi-Touch Attribution in Online Advertising with Survival Theory.
\bibitem{survival_sol_1}
Wendi Ji, Xiaoling Wang and Dell Zhang (2016), A Probabilistic Multi-Touch Attribution Model for Online Advertising
\bibitem{MLE_convergence}
Fritz Scholz (1996, revised on 2001), Maximum Likelihood Estimation for Type I Censored Weibull Data Including Covariates


\bibitem{fbprophet}
Sean J. Taylor, Benjamin Letham (2017),  Forecasting at Scale. 
\end{thebibliography}